Cloud Supercomputing with the ExaHyPE-Engine\\Master Thesis Kick-Off

### 2018-10-18 writing/slides/kick_off.tex
Revise kick off slides, final(?) revision.
Also add conv. plot.
Add final (really?) version of slides.

\title{Cloud Supercomputing with the ExaHyPE-Engine\\Master Thesis Kick-Off}
\author{Lukas Krenz\\Adviser: Leonhard Rannabauer\\Superviser: Prof.\ Dr.\ Michael Bader}
\date{October 18, 2018} 
\institute{\textsc{tum}, Chair for Scientific Computing}

@@

Implemented in the PDE-Framework \textbf{ExaHyPE}.
\end{frame}

@@

Flux:
\begin{equation}
  F(Q, \textcolor{orange}{\nabla Q}) = 
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q)}  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q))} -
    \textcolor{orange}{\kappa \nabla T}
  \end{pmatrix}
\end{equation}

@@

\begin{frame}{Problem: Not hyperbolic}
  DG solves equations of the form (e.g.\ Euler):
  \begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
\end{equation}

@@

\textbf{Solution}:
Modify numerical flux (Riemann solver), time step size (CFL-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary}.

@@

  \begin{block}{Goals}
  \begin{itemize}
  \item Fix convergence
  \item Adaptive Grids
  \item Finite Volume Limiting\footfullcite{dumbser2016simple}
  \item Coupling of Navier-Stokes with other PDE (e.g.\ simple advection equation) by solving Riemann problem at boundary
  \end{itemize}
  \end{block}
\end{frame}

% \begin{frame}{Current status of Convergence-Tests}
%   \begin{figure}[h]
%     \centering
%    \includegraphics[width=0.8\textwidth]{{l2_error}}
%     \caption{Mesh-Size vs $L_2$ error }
%     \label{fig:l2-error}
%   \end{figure}
% \end{frame}

@@

  \begin{block}{Bonus Objectives}
    \begin{itemize}
    \item All extensions to engine (diffusive fluxes, coupling) useful for other user of ExaHyPE.
    \item First use of ExaHyPE-Engine for simulation of clouds.
    \end{itemize}

>>>>

\title{Cloud Supercomputing with the ExaHyPE-Engine\\Master Thesis Kick-Off}
\author{Lukas Krenz\\Adviser: Leonhard Rannabauer\\Supervisor: Prof.\ Dr.\ Michael Bader}
\date{October 18, 2018} 
\institute{\textsc{tum}, Chair for Scientific Computing}

@@

Implemented in the \textsc{PDE}-Framework \textbf{ExaHyPE}.
\end{frame}

@@

Flux:
\begin{equation}
  F(Q, \textcolor{orange}{\nabla Q}) = 
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q)}  \\
    \Qv \cdot \left(\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q)} \right) -
    \textcolor{orange}{\kappa \nabla T}
  \end{pmatrix}
\end{equation}

@@

\begin{frame}{Problem: Not hyperbolic}
  \textsc{DG} solves equations of the form (e.g.\ Euler):
  \begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
\end{equation}

@@

\textbf{Solution}:
Modify numerical flux (Riemann solver), time step size (\textsc{cfl}-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary}.

@@

  \begin{block}{Goals}
  \begin{itemize}
  \item Fix convergence
  \item Adaptive Mesh Refinement
  \item Finite Volume Limiting\footfullcite{dumbser2016simple}
  \item Coupling of Navier-Stokes with other PDE (e.g.\ simple advection equation) by solving Riemann problem at boundary
  \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Current status of Convergence-Tests}
  \begin{figure}[h]
    \centering
   \includegraphics[width=0.8\textwidth]{{l2_error}}
    \caption{Mesh-Size vs $L_2$ error }
    \label{fig:l2-error}
  \end{figure}
\end{frame}

@@

  \begin{block}{Bonus Objectives}
    \begin{itemize}
    \item All \textbf{extensions} to engine (diffusive fluxes, coupling) useful for \textbf{other users} of ExaHyPE.
    \item First use of ExaHyPE-Engine for \textbf{simulation of clouds}.
    \end{itemize}
